---
output: github_document
---


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "99%"
)
```

# DiscGolf package


The goal of this package is to provide an example of how to create a data package in R.

It uses Nick's example from the DataIsPlural website to tell people about approved discs for disc golf.

See https://youtu.be/-VHYLgEBzNc for a Youtube video and the files in https://github.com/nicholasjhorton/DiscGolf/tree/master/DiscGolf_files for more information. 

## Installation

Want to try it?
You can install the package from [GitHub](https://github.com/) with:

```{r eval = FALSE}
# install.packages("remotes")
remotes::install_github("nicholasjhorton/DiscGolf")
```
## Example

This could be where you provide a basic example which shows you how to solve a common problem:

```{r example}
library(DiscGolf)
summary(DiscGolf)
head(DiscGolf)
sessionInfo()
```

Last updated October 11, 2023
